
\section{Introduction}
\label{sec:intro}
\noindent
This bootcamp is aimed at scientific researchers who are familiar with
functional programming in python but are not necessarily experts therein.
Functional programming in general encompasses all practices and techniques
short of object-oriented programming, i.e., functions (\textit{def}), loops
(\textit{for} and~\textit{while}), and conditional statements (\textit{if},
\textit{elif}, and~\textit{else}) combined with various data types.
Though exception handling (\textit{try},~\textit{except}, and~\textit{finally})
and multi-file programs (i.e., packages) technically fall under this category
as well, refined skills in these techniques are less common among researchers.
% This bootcamp therefore aims to deepen the typical scientist's knowledge of
% functional programming in this way before introducing them to object-oriented
% programming.
\par
The ultimate goals of this curriculum are to review the concepts of functional
programming and introduce the participants to the Unix terminal, python
packages, and object-oriented programming.
As a bootcamp, the material is much more condensed than if it were presented in
the format of a traditional semester-long course.
Consequently, the instruction proceeds sufficiently fast that most participants
are still learning a given set of concepts and techniques before the next
session presents them with an entirely new set.
Mastery is almost never achieved in the timespan of the bootcamp itself and
instead arrives on longer timescales as the participants apply the concepts
they learn to their research project code bases.\footnote{
	Instructors are recommended to make this reality clear to the participants
	at the beginning.
}
\par
In practice, the target audience for this bootcamp is most often the
participants of the Summer Undergraduate Research Program (SURP).
Each year, SURP is dominated by students entering their third and fourth years
of the major.
Most of these students have received some level of instruction in python from
ASTRON 1221 (\textit{Astronomy Data Analysis}) and ASTRON 3350 (\textit{Methods
of Astronomical Observation \& Data Analysis}), which places the typical
participant at exactly the level of familiarity with functional programming
appropriate for this bootcamp.
With instruction in object-oriented programming, however, the curriculum has
proved useful for scientists of all levels of seniority, including tenured
faculty members (whether or not they have the time to participate is, however,
a different question entirely).
As a result, each session is generally open to all membes of the Departments of
Physics and Astronomy, even the SURP students are the primary participants.
The instructional material can be easily modified to accommodate an audience
dominated by more experienced researchers (e.g., graduate students) by simply
shifting emphasis between different topics.

